\chapter{Graph}

\section{Alien Dictionary} %%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Description}
There is a new alien language which uses the latin alphabet. However, the order among letters are unknown to you. You receive a list of non-empty words from the dictionary, where words are sorted lexicographically by the rules of this new language. Derive the order of letters in this language.

\textbf{Example:}

Given the following words in dictionary,
\begin{Code}
[
  "wrt",
  "wrf",
  "er",
  "ett",
  "rftt"
]
\end{Code}

The correct order is: \code{"wertf"}.

\textbf{Note:}

1. You may assume all letters are in lowercase.

2. You may assume that if a is a prefix of b, then a must appear before b in the given dictionary.

3. If the order is invalid, return an empty string.

4. There may be multiple valid order of letters, return any one of them is fine.

\newpage

\subsubsection{Solution}

\begin{Code}
public String alienOrder(String[] words) {
    int[] indegree = new int[26];
    Arrays.fill(indegree, -1);

    int count = 0;
    for (String word : words) {
        for (char c : word.toCharArray()) {
            if (indegree[c - 'a'] != 0) {
                indegree[c - 'a'] = 0;
                count++;
            }
        }
    }
    HashMap<Character, Set<Character>> map = new HashMap<>();
    for (int i = 0; i < words.length - 1; i++) {
        String first = words[i], second = words[i + 1];
        int len = Math.min(first.length(), second.length());
        for (int j = 0; j < len; j++) {
            if (first.charAt(j) != second.charAt(j)) {
                Set<Character> set = map.get(first.charAt(j));
                if (set == null) {
                    set = new HashSet<Character>();
                    map.put(first.charAt(j), set);
                }
                if (set.add(second.charAt(j))) {
                    indegree[second.charAt(j) - 'a']++;
                }
                break;
            } else {
                if (j + 1 >= second.length() && j + 1 < first.length()) { return ""; }
            }
        }
    }
    Queue<Character> queue = new LinkedList<Character>();
    for (int i = 0; i < indegree.length; i++) {
        if (indegree[i] == 0) {
            queue.add((char) ('a' + i));
        }
    }
    StringBuilder sb = new StringBuilder();
    while (!queue.isEmpty()) {
        Character from = queue.poll();
        sb.append(from);
        Set<Character> set = map.get(from);
        if (set != null) {
            for (Character to : map.get(from)) {
                if (--indegree[to - 'a'] == 0) {
                    queue.add(to);
                }
            }
        }
    }
    return sb.length() != count ? "" : sb.toString();
}
\end{Code}